---
name: William Kyle
surname: Belanger
position: "Field Application Specialist"
address: "435 Gibson Dairy Road, Elizabethtown NC 28337"
phone: 843-455-5122
www: kyleb.rbind.io
email: "wkbelanger0526@email.campbell.edu"
github: mmmmtoasty19
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(here)
library(lubridate)
library(tibble)

```

```{r jobs, include=FALSE}
jobs.raw <- read.csv(here::here("data", "jobs.csv"),na.strings = "")
jobs <- jobs.raw %>% 
  fill(start,end,what,with,where,why) %>% 
  mutate(
    start = mdy(start)
    ,end = mdy(end)
  ) %>% 
  mutate( when = case_when(
    is.na(end) ~ glue::glue("{year(start)}--Present") %>% as.character(),
    year(start) == year(end) ~ year(end) %>% as.character(),
    TRUE ~ glue::glue("{year(start)}--{year(end)}") %>% as.character()
  ))



jobs %>%  glimpse()
```

# About Me
  I am a highly skilled Medical Technologist, with a passion for Data Science and Visualization.  I bring with me 11 years of experience in the medical world, and understand what is needed for proper data analysis.  I have manged employees in the past, and worked on both large and small project teams. I am focused on bridging the gap between medical personnel and information technologists.

# Technical Skills
 - Data Analysis
 - Data Visualization
 - Intermediate level in R
 - Basic Understanding of Python and SQL
 - Highly skilled in Microsoft Office

# Education

```{r}
readr::read_csv("../data/education.csv") %>% 
  brief_entries(Degree, Year, Institution)

```

# Jobs

```{r}
detailed_entries(jobs
                 ,what  = what
                 ,when  = when
                 ,with  = with
                 ,where = where
                 ,why   = why)
```

# Professional Licenses

```{r}
tribble(
  ~ Institution,~ Year, ~ With
  ,"ASCP", "2010 - Present", "Medical Laboratory Scientist"
) %>% 
  brief_entries(Institution,Year,With)
```



# References
  
  Available on request